%-------------------------
% Resume in Latex
% Author : Elufioye Michael
% Based off of: https://github.com/michgboxy2
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Elufioye Michael} \\ \vspace{1pt}
    \small $|$ \href{mailto:michgboxy@gmail.com}{\underline{michgboxy@gmail.com}} $|$ 
    \href{https://linkedin.com/in/michgboxy}{\underline{linkedin.com/in/michgboxy}} $|$
    \href{https://github.com/michgboxy2}{\underline{github.com/michgboxy2}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Obafemi Awolowo University}{Ile-fe}
      {Departments of Biochemistry}{Aug. 2009 -- Nov 2013}
  
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Tizeti inc (YC 17)}{December 2023 -- Present}
      {Senior Backend Developer}{Lagos}
      \resumeItemListStart
          \resumeItem{Designed and developed \textbf{TizetiOS}, the core operational software powering Tizeti's business operations across Nigeria, Ghana, and Côte d'Ivoire.}
          \resumeItem{Implemented critical modules such as billing, invoicing, and payroll systems to streamline internal processes for the account and admin team.}
          \resumeItem{Led the development of \textbf{Wificall} using \textbf{Node.js, PHP, Asterisk, RabbitMQ, Redis, MySQL, React} within a microservice architecture, a web and mobile VoIP product enabling seamless voice-over-IP communication.}
          \resumeItem{Developed an automated billing system using \textbf{Node.js, MongoDB} that powers the customer billing for Tizeti services.}
          \resumeItem{Engineered a comprehensive DevOps and monitoring stack using \textbf{Jenkins} for CI/CD and \textbf{Docker Swarm} for orchestration; integrated monitoring with self-hosted \textbf{Jaeger, Loki, Promtail, Prometheus}, and \textbf{Grafana}.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Nursedash}{Nov. 2020 -- Nov. 2023}
      {Senior Software Engineer}{USA}
      \resumeItemListStart
          \resumeItem{Built the \textbf{Nursedash Reliability System} to rank clinicians based on effectiveness and reliability, enabling leadership to identify top performers across the workforce.}
          \resumeItem{Designed and developed the \textbf{Auto-Select System} using \textbf{Nodejs, GraphQL, Postgres, BullMQ}, an intelligent shift matching engine that automates selection and approval from thousands of shift applications. It monitors applicant confirmations and reassigns unconfirmed shifts, resulting in a \textbf{7\% month-over-month increase} in shift completion rates.}
          \resumeItem{Developed the \textbf{payment infrastructure} responsible for clinician payouts post-shift completion and automated reconciliation for the payroll team.}
          \resumeItem{Engineered the \textbf{Daily pay system} responsible for improving the clinician payout time from weekly to daily.}
          \resumeItem{Re-architected the Nursedash backend into a \textbf{microservices architecture} to enhance scalability and performance. Integrated \textbf{Kafka} for background job queuing and \textbf{Redis} caching to reduce database load and increase response time.}
          \resumeItem{Led backend performance optimization efforts using \textbf{Redis}, \textbf{Kafka}, and \textbf{microservices}, significantly improving system reliability during peak loads.}
          \resumeItem{Managed \textbf{DevOps infrastructure}, implementing CI/CD pipelines using \textbf{GitHub Actions}, container orchestration with \textbf{Docker} and \textbf{Kubernetes}, and deployment automation.}
      
    \resumeItemListEnd

    \resumeSubheading
      {Senior software developer (contract)}{April 2020 -- Sep 2020}
      {StealthRever analytics}{Boston, USA}
      \resumeItemListStart
        \resumeItem{Contributed to the design and development of \textbf{Pharmedge}, a global pharmaceutical supply chain platform providing direct access between hospitals and pharmaceutical manufacturers, reducing costs and improving accessibility for end consumers.}
        \resumeItem{Led the development of key modules including inventory management, purchasing, bidding, and multi-carrier global shipping and logistics.}
        \resumeItem{Implemented scalable backend systems using \textbf{Node.js}, \textbf{Express}, and \textbf{AWS Serverless} architecture (\textbf{Lambda, DynamoDB, EC2}).}
        \resumeItem{Engineered the development of a multi-carrier global shipping and monitoring logisitic infrastructure}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


  \resumeSubheading
     {Software developer (contract)}{Jan 2020 -- April 2020}
     {Rentzend}{San Francisco, CA}
     \resumeItemListStart
      \resumeItem{Contributed to the engineering of \textbf{Rentzend}, a San Francisco-based startup focused on tenancy placement and real estate rental market analysis.}
      \resumeItem{Built a web scraping system using \textbf{Puppeteer} and \textbf{Cheerio} to gather and compare global real estate pricing and availability, enabling accurate rental projections and data-driven decisions.}
      \resumeItem{Designed and implemented backend services using \textbf{Node.js}, \textbf{Koa}, and \textbf{Apollo GraphQL}, supporting dynamic user queries and analysis features.}
      \resumeItem{Developed the frontend using \textbf{React.js}, \textbf{Next.js}, and \textbf{React Apollo} for interactive data visualization and user dashboards.}
      \resumeItem{Wrote end-to-end and unit tests using \textbf{JEST} and \textbf{Cypress} to ensure system reliability and robustness.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd

  \resumeSubheading
  {Backend Engineer (Contract)}{Dec 2017 -- May 2019}
  {NOUVEAU RICHE MEDIA TECHNOLOGY}{Lagos, Nigeria}
  \resumeItemListStart
    \resumeItem{Engineered the backend system of the bank's \textbf{Internet Banking Application} enabling customers to perform inter/intra-bank transfers, airtime purchases, and bill payments.}
    \resumeItem{Designed and implemented a scalable \textbf{microservice architecture} using \textbf{Node.js}, \textbf{Express}, and \textbf{GraphQL} with \textbf{Apollo Server} for seamless API integration.}
    \resumeItem{Integrated \textbf{RabbitMQ} to manage asynchronous tasks, improving system responsiveness and reducing request load.}
    \resumeItem{Implemented \textbf{Redis} caching to reduce database load and improve transaction speed.}
    \resumeItem{Worked with \textbf{MySQL} and \textbf{MongoDB} for structured and flexible data storage.}
    \resumeItem{Performed \textbf{unit and end-to-end testing} using \textbf{Mocha}, \textbf{Chai}, and \textbf{Supertest} to ensure application stability and performance.}
    \resumeItem{Collaborated with the frontend team using \textbf{React.js}, \textbf{Redux}, and \textbf{Apollo Client} to deliver a smooth customer experience.}
  \resumeItemListEnd

  \resumeSubheading
  {Software Developer (Independent Contractor)}{May 2017 -- Dec 2017}
  {Great Brands Limited}{Lagos, Nigeria}
  \resumeItemListStart
    \resumeItem{Led the development of a high-performance \textbf{logistics application} for real-time tracking of company vehicles, route efficiency monitoring, and mileage analysis.}
    \resumeItem{Contributed to the development of \textbf{Sunrise}, an eCommerce platform that digitized the company’s retail operations by automating product ordering, checkout, and delivery workflows for distributors.}
    \resumeItem{Implemented inventory monitoring and warehouse tracking systems across nationwide retail outlets.}
    \resumeItem{Developed the monolithic backend using \textbf{Node.js}, \textbf{Express}, and followed a test-driven development (TDD) approach.}
    \resumeItem{Built the frontend in \textbf{React.js} with \textbf{Redux} for state management and integrated APIs to support seamless data flow.}
    \resumeItem{Performed unit and end-to-end testing using \textbf{Mocha}, \textbf{Jest}, \textbf{Enzyme}, and \textbf{Supertest}.}
    \resumeItem{Utilized \textbf{MySQL} for relational data, \textbf{Redis} for caching, and \textbf{Elasticsearch} to implement fast and scalable search features.}
    \resumeItem{Implemented CI/CD pipelines using \textbf{CircleCI} for continuous integration and deployment.}
  \resumeItemListEnd

  \resumeSubheading
  {Software Developer}{Jan 2016 -- Apr 2017}
  {Eazyhire}{Lagos, Nigeria}
  \resumeItemListStart
    \resumeItem{Contributed to the development of \textbf{Eazyhire}, Africa’s leading fully insured peer-to-peer sharing and leasing platform.}
    \resumeItem{Helped build the core \textbf{E-commerce platform} that enables users to list, hire, and lease products with payment, delivery, and return tracking.}
    \resumeItem{Developed backend functionalities using \textbf{Laravel}, ensuring efficient product listing, leasing workflows, and user transactions.}
    \resumeItem{Implemented and optimized data storage and retrieval with \textbf{MySQL} for high performance and data integrity.}
  \resumeItemListEnd


-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Oyapost (https://oyapost.com)} \href{mailto:michgboxy@gmail.com} $|$ \emph{Nextjs, React, Golang PostgreSQL, Docker}}{May 2025 -- Present}
          \resumeItemListStart
            \resumeItem{Developed a full-stack social media scheduling tool using with Golang Backend and React/Nextjs frontend, the application schedules content to X/twitter, Tiktok, Threads, Instagram, Facebook, Pinterest, Reddit, Youtube}
            \resumeItem{Implemented the automated Key rotating to prevent authorized keys from expiring and prevent users from having to re-authorize}
            \resumeItem{Used Loki, Grafana, Prometheus, Promtail, Jaeger fro tracing and monitoring}
            \resumeItem{Used Asynq for asynchronous tasks}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Nodejs, PHP, Javascript, Golang, GraphQL, Typescript} \\
     \textbf{Frameworks}{: React, Node.js, Express, Koa, Vue, Laravel, ReactNative, Microservices} \\
     \textbf{Developer Tools}{: Docker, Kubernetes, ElasticSearch, Kafka, RabbitMQ} \\
     \textbf{Database}{: MySQL, PostgreSQL, MongoDB, Redis} \\
     \textbf{Cloud expertise}{: AWS, GCP, MongoDB, Azure} \\
     \textbf{Devops tools}{: Kubernetes, Docker, Github actions, Jenkins, Shell scripting, Bash scripting, Jaegar, Loki, Promtail, Grafana, Prometheus}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
