%-------------------------
% Resume in Latex
% Author : Elufioye Michael
% Based off of: https://github.com/michgboxy2
% Repurposed for Technical Product Manager by Gemini
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Elufioye Michael} \\ \vspace{1pt}
    \small Technical Product Manager \\ \vspace{4pt}
    \small $|$ \href{mailto:michgboxy@gmail.com}{\underline{michgboxy@gmail.com}} $|$ 
    \href{https://linkedin.com/in/michgboxy}{\underline{linkedin.com/in/michgboxy}} $|$
    \href{https://github.com/michgboxy2}{\underline{github.com/michgboxy2}}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
\small{A results-oriented Technical Product Manager with over 8 years of experience translating complex technical challenges into market-leading products. Proven ability to own the entire product lifecycle, from ideation and roadmapping to launch and iteration. Expert in collaborating with engineering, design, and business teams to deliver user-centric solutions that drive revenue growth and improve operational efficiency. Deeply skilled in agile methodologies, data-driven decision-making, and bridging the gap between technical implementation and strategic business goals.} \\


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Obafemi Awolowo University}{Ile-Ife, Nigeria}
      {B.Sc., Departments of Biochemistry}{Aug. 2009 -- Nov. 2013}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Tizeti inc (YC 17)}{Lagos, Nigeria}
      {Senior Technical Product Manager}{December 2023 -- Present}
      \resumeItemListStart
        \resumeItem{Defined the product vision, strategy, and roadmap for \textbf{TizetiOS}, the core operational software powering business across Nigeria, Ghana, and Côte d'Ivoire.}
        \resumeItem{Translated business needs from finance and admin teams into product requirements for critical billing, invoicing, and payroll modules, improving operational efficiency.}
        \resumeItem{Led the end-to-end product development of \textbf{Wificall}, a VoIP product, from concept and technical design to market launch, utilizing a microservice architecture.}
        \resumeItem{Drove the product strategy for an automated billing system, resulting in improved accuracy and scalability of customer billing for Tizeti services.}
        \resumeItem{Ensured product reliability and performance by championing a comprehensive DevOps and monitoring stack, leading to enhanced system uptime and data-driven incident response.}
      \resumeItemListEnd

    \resumeSubheading
      {Nursedash}{USA (Remote)}
      {Senior Product Manager, Technical}{Nov. 2020 -- Nov. 2023}
      \resumeItemListStart
        \resumeItem{Conceptualized and delivered the \textbf{Nursedash Reliability System}, a data-driven product that enabled leadership to identify and reward top-performing clinicians.}
        \resumeItem{Owned the product roadmap for the \textbf{Auto-Select System}, an intelligent matching engine that automated shift assignments and increased shift completion rates by \textbf{7\% month-over-month}.}
        \resumeItem{Led the product strategy for the payment infrastructure, launching a \textbf{Daily Pay system} that reduced clinician payout times from weekly to daily, boosting user satisfaction.}
        \resumeItem{Spearheaded the strategic migration to a \textbf{microservices architecture}, defining technical requirements to enhance product scalability and performance during peak loads.}
        \resumeItem{Managed the product backlog and prioritized features for the backend platform, leveraging \textbf{Redis}, \textbf{Kafka}, and \textbf{microservices} to improve system reliability.}
      \resumeItemListEnd

    \resumeSubheading
      {StealthRever analytics}{Boston, USA (Contract)}
      {Technical Product Manager}{April 2020 -- Sep. 2020}
      \resumeItemListStart
        \resumeItem{Contributed to the product strategy and feature definition for \textbf{Pharmedge}, a global pharmaceutical supply chain platform connecting hospitals directly with manufacturers.}
        \resumeItem{Translated market needs into technical requirements for key modules including inventory management, purchasing, and multi-carrier global logistics.}
        \resumeItem{Collaborated with engineering to deliver a scalable backend using \textbf{AWS Serverless} architecture, reducing operational costs and improving platform accessibility.}
      \resumeItemListEnd

    \resumeSubheading
     {Rentzend}{San Francisco, CA (Contract)}
     {Product-Focused Software Engineer}{Jan 2020 -- April 2020}
     \resumeItemListStart
      \resumeItem{Informed product strategy by engineering a web scraping system to gather and analyze global real estate pricing, enabling data-driven rental projections.}
      \resumeItem{Collaborated on backend service design using \textbf{Node.js}, \textbf{Koa}, and \textbf{GraphQL} to support dynamic data visualization and user analysis dashboards.}
      \resumeItem{Worked with the product team to define requirements for frontend features, ensuring alignment between user needs and technical implementation.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Oyapost (https://oyapost.com)} $|$ \emph{Next.js, React, Golang, PostgreSQL, Docker}}{May 2025 -- Present}
          \resumeItemListStart
            \resumeItem{Acting as Product Owner for a full-stack social media scheduling tool; defining the product roadmap, user stories, and feature prioritization.}
            \resumeItem{Designing product features such as automated key rotation to enhance user experience by preventing service interruptions.}
            \resumeItem{Implementing a data-driven approach using monitoring tools (\textbf{Loki, Grafana, Prometheus}) to track performance and guide product iterations.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Product Management}{: Agile \& Scrum, Product Roadmapping, Lifecycle Management, Stakeholder Management, Data Analysis, User-Centric Design, A/B Testing, Competitive Analysis} \\
     \textbf{Languages}{: Node.js, Golang, PHP, Javascript, Typescript, SQL, GraphQL} \\
     \textbf{Architecture \& Systems}{: Microservices, Event-Driven Architecture, API Design, System Design} \\
     \textbf{Developer Tools}{: Docker, Kubernetes, Kafka, RabbitMQ, Jenkins, Git, Jaeger, Grafana, Prometheus} \\
     \textbf{Cloud \& Databases}{: AWS, GCP, Azure, PostgreSQL, MySQL, MongoDB, Redis}
    }}
 \end{itemize}

%-------------------------------------------
\end{document}